\documentclass[memo]{corpboreport}

\AllowUndeclaredYV

%! language = yaml
\begin{parseYAMLvars}
subject: Something to Worry About

date: \today

fileno: 420---69

attachments: test
#  - [Some Url, www.google.ca]  # todo make urls

memoFr:
  - Kale Ewasiuk
  - \GIP
  - \IRP
  - \TBU
  - pooper

memoTo:
  - Steve Shelemy
  - \GIP
  - \IRP
  - \TBU

memoHeader: Manitoba Hydro -- Interoffice Memorandum

GIP: Grid Infrastructure Planning Dept.
IRP: Integrated Resource Planning Div.
TBU: Transmission Business Unit
\end{parseYAMLvars}



\begin{document}


	% https://tex.stackexchange.com/questions/4805/whats-the-correct-use-of-author-when-multiple-authors
	% https://tex.stackexchange.com/questions/466095/redefine-title-for-possibility-of-a-forced-line-breaking-in-a-predefined-place


%
%\makeatletter
%
%\thispagestyle{plain}
%\vspace*{-4.5em}
%
%\ifdef{\@memoHeader}{\vspace*{-2em}  \ \hfill {\large\bfseries \@memoHeader } \hfill \  \\[1.2em]}
%
%\begin{tabularx}{\linewidth}{@{}lXl@{}}
%	\@HangingLabel{to}\textit{\@memoToA}  &&
%	\@HangingLabel{fr}\textit{\@memoFrA}\\ \noalign{\vskip 0.5mm} % add a bit more space %%% todo need an ifdefOR{\cs1}{\cs2}{}{}
%
%	\ifdefOR{\@memoToB}{\@memoFrB}{\ifdef{\@memoToB}{\@memoToB}{}	&&   \ifdef{\@memoFrB}{\@memoFrB}{}	 \\}{}
%	\ifdefOR{\@memoToC}{\@memoFrC}{\ifdef{\@memoToC}{\@memoToC}{}	&&   \ifdef{\@memoFrC}{\@memoFrC}{}	 \\}{}
%	\ifdefOR{\@memoToD}{\@memoFrD}{\ifdef{\@memoToD}{\@memoToD}{}	&&   \ifdef{\@memoFrD}{\@memoFrD}{}	 \\}{}
%	\ifdefOR{\@memoToE}{\@memoFrE}{\ifdef{\@memoToE}{\@memoToE}{}	&&   \ifdef{\@memoFrE}{\@memoFrE}{}	 \\}{}
%
%	\\\noalign{\vskip -1.3ex}
%	\midrule
%\end{tabularx}
%
%\vspace{1em}
%%
%\parbox{\linewidth}{\setstretch{1.3}
%	\ifdef{\@subject}{\@HangingLabel{subject}\raggedright\textbf{\Large\@subject}\\[8pt]}{}%
%	\ifdef{\@date}{\@HangingLabel{date}\textbf{\Large\@date}\\[8pt]}{}
%	\ifdef{\@fileno}{\@HangingLabel{file}\textbf{\Large\@fileno}\\[8pt]}{}
%	\ifdef{\@attachments}{\@HangingLabel{attached}\@attachments\\[8pt]}{}
%	\par
%}%
%
%
%\makeatother

%  \makeMemotitle

\section{Introduction}

todo modify smash on graphics insertion for title page alignment

A Corporate-Friendly Boring Template.

This class is based off the scrartcl class in the KOMA-Script family.
Don't let the name fool you---although plain and unassuming with a (dare I say) Word-like appearance,
this template has a few bells and whistles that make your TeXing easier.
It could easily lend itself well to school assignments or lab reports,

\section{Quick start guide}

\section{Options}
Memo
Serif

\section{Sections}

This format uses KOMA script, so any commands are fair-game.

This class by default will insert a page break on a new section.
Using the etoolbox package, you can disable this behaviour.

if you want to invert the behaviour for a particular section, use !

For paragraphs, if you would like the text to appear on a new line (rather than run in), use !.



todo use AtBeginDocument and AtEndDocument -- do at end for  end of memo/report

\section{Tweaking the format}

\section{Float commands}

\section{Tabular commands}

\section{List commands}

\section{Dependencies}

\PrintEndOfDocument*

\end{document}